paper2_resistance_mechanisms_mixtures

### 2016-05-20 inst/documents/effectOfIndividualInputs.Rmd
moved documents into own folder

  #1) sequential : time to resistance for each insecticide in isolation
  #inputs : inAndOutI1, inAndOutI2
  #find time to criticalPoint for insecticide1
  #find time to criticalPoint for insecticide2
  #add together
  resistPointsI1 <- findResistancePoints(listOutI1, locus=1)
  resistPointsI2 <- findResistancePoints(listOutI2, locus=2)

  resistPointsSeq <- resistPointsI1 + resistPointsI2

@@

  #ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point() + facet_wrap( ~ cut)

  #cool working!

  #exposure has the most noticeable effect
  ggplot(ggInsOuts, aes(x=exposure, y=time_to_resistance0.25, color=strategy)) + 
    geom_point(shape=3) + 
    facet_wrap( ~ strategy) + 
    #geom_smooth(aes(x=exposure, y=gen_cP0.5, color=NULL))
    geom_smooth(colour='red', linetype='dashed',size=0.5)

  #effectiveness of insecticide1 little noticeable effect
#   ggplot(ggInsOuts, aes(x=effectiveness_insecticide1, y=time_to_resistance0.25, color=strategy)) + 
#     geom_point() + 
#     facet_wrap( ~ strategy) + 
#     #geom_smooth(aes(x=effectiveness_insecticide1, y=gen_cP0.5, color=NULL)) 
#     geom_smooth(colour='red', linetype='dashed',size=0.5)

@@

## In the following plots all inputs are plotted individually, the points are coloured by exposure, which allows us to see that, even as other inputs change, low times to resistance are associated with high exposure.
```{r, eval=TRUE, echo=FALSE, fig.height=3.5}

    y <- 'time_to_resistance0.25'    
    #y <- 'time_to_resistance0.5'
    #color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    color <- 'exposure'

    print( ggplot(ggInsOuts, aes_string(x=i, y=y, color=color)) + 
             geom_point(shape=3) + 
             facet_wrap( ~ strategy) + 
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             geom_smooth(colour='red', linetype='dashed',size=0.5) +
             labs(title = i))
  }

  #can I facet by particular parameter ranges ?
  #might need to create a categorical var from the range and use that to facet 
  #or subset the data for specific parameter ranges

## Looking more closely at effect of the ratio between the level of resistance to the first insecticide divided by that of the second one. Restricting the x axis to lower values.
```{r, eval=TRUE, echo=FALSE, warning=FALSE}

@@

```{r, eval=FALSE, echo=FALSE, warning=FALSE, fig.height=3.5}

#trying to find apparent anomaly in PRCC analysis
#what causes correctMixDeployProp to get a high PRCC score for I1 & 2 when its not used in those runs ??

tstI1 <- round(listOutI1$input,3)
tstMix <- round(listOutMix$input,3)
tstDif <- round(tstMix - tstI1,3)

@@

>>>>

  #1) sequential : time to resistance for each insecticide in isolation
  #inputs : inAndOutI1, inAndOutI2
  #find time to criticalPoint for insecticide1
  #find time to criticalPoint for insecticide2
  #add together
  resistPointsI1 <- findResistancePoints(listOutI1, locus=1)
  resistPointsI2 <- findResistancePoints(listOutI2, locus=2)  
  resistPointsSeq <- resistPointsI1 + resistPointsI2

@@

@@

# Plot time to resistance for each strategy using all sensitivity analysis values
```{r, eval=TRUE, echo=FALSE, warning=FALSE}

names_results <- c("time_to_resistance0.5","time_to_resistance0.25","time_to_resistance0.1")

for(i in names_results)
{
  #x11()

  print( ggplot(ggInsOuts, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      coord_cartesian(xlim=c(1, 6), ylim=c(0, 350)) +
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE)
  )#end print
}

  #can I facet by exposure ?
  #exposure <- runif(1, min=0.1, max=0.9)
  #why does it not look uniform ? must be because runs have been removed if too high
  hist(ggInsOuts$exposure)
  #create exposure bins
  ggInsOuts$exposure_cat <- cut(ggInsOuts$exposure,breaks=c(0.1,0.3,0.5,0.7,0.9), labels=c("exposure 0.1-0.3","exposure 0.3-0.5","exposure 0.5-0.7","exposure 0.7-0.9"))
  #or just 2
  #ggInsOuts$exposure_cat <- cut(ggInsOuts$exposure,breaks=c(0.1,0.5,0.9), labels=c("exposure 0.1-0.5","exposure 0.5-0.9"))
  #actually might be better to show just the 2 extremes
  #ggSubset <- subset(ggInsOuts, exposure_cat==c("exposure 0.1-0.3","exposure 0.7-0.9"))

  print( ggplot(ggInsOuts, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      #scale_y_continuous( limits = c( 0,450 ) ) +
      #to zoom in without changing data  
      coord_cartesian(xlim=c(1, 6), ylim=c(0, 350)) +
      facet_wrap( ~ exposure_cat, scales='fixed') +  
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) #, scale='count')
  )#end print

# or trying as a dotplot, with these options it's very similar to violin
#   print( ggplot(ggInsOuts, aes_string(x='strategy',y=i, color='strategy')) + 
#       #ylim(0,450) +
#       scale_y_continuous( limits = c( 0,450 ) ) +
#       facet_wrap( ~ exposure_cat, scales='fixed') +  
#       geom_dotplot(stackdir = 'center', binaxis='y', binwidth = 5 ,dotsize = 0.1, show.legend=FALSE) #, scale='count')
#   )#end print

#now try the same faceting by effectiveness_insecticide1
#doesn't really show much ...
#so why does effectiveness come out so important in the trees ??  
  #hist(ggInsOuts$effectiveness_insecticide1)  
  #create effect1 bins
  ggInsOuts$effect1_cat <- cut(ggInsOuts$effectiveness_insecticide1,breaks=c(0.4,0.6,0.8,1), labels=c("effect1 0.4-0.6","effect1 0.6-0.8","effect1 0.8-1"))

  print( ggplot(ggInsOuts, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      #scale_y_continuous( limits = c( 0,450 ) ) +
      #to zoom in without changing data  
      coord_cartesian(xlim=c(1, 6), ylim=c(0, 250)) +
      facet_wrap( ~ effect1_cat, scales='fixed', nrow=1) +  
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) #, scale='count')
  )#end print

## BEWARE what am I doing with putting mixture better than seq on each repeated input ....

## !!try facetting by whether mixture or sequence better
## initially just with the time to resistance
## relies on ggInsOuts being prepared slightly differently from sensiAnPaper1All
## aha! this is weird it actually shows much shorter times for mixture1, & mix2 but sequential fairly similar  
#   print( ggplot(ggInsOuts, aes_string(x='strategy',y=i, color='strategy')) + 
#       #ylim(0,450) +
#       #scale_y_continuous( limits = c( 0,450 ) ) +
#       #to zoom in without changing data  
#       coord_cartesian(xlim=c(1, 6), ylim=c(0, 250)) +
#       facet_wrap( ~ betterMix2Seq20_cP0.1, scales='fixed', nrow=1) +  
#       geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) #, scale='count')
#   )#end print

# or I could look at the values for exposure on the y axis
#   print( ggplot(ggInsOuts, aes_string(x='strategy',y='exposure', color='strategy')) + 
#       #ylim(0,450) +
#       #scale_y_continuous( limits = c( 0,450 ) ) +
#       #to zoom in without changing data  
#       #coord_cartesian(xlim=c(1, 6), ylim=c(0, 250)) +
#       facet_wrap( ~ betterMix2Seq20_cP0.1, scales='fixed', nrow=1) +  
#       geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) #, scale='count')
#   )#end print

@@

## trying to highlight differences between sequential and mixture strategies in response of time-to-resistance to inputs
```{r, eval=TRUE, echo=FALSE, fig.height=3.5}

  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]

    y <- 'time_to_resistance0.25'

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1.5) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i))
  }

@@

## response of resistance thresholds to individual inputs faceted by strategy
```{r, eval=TRUE, echo=FALSE, fig.height=3.5}

  #todo find out to take sample this doesn't work
  #ggSample <- sample(ggInsOuts,500)

    y <- 'time_to_resistance0.25'    
    #y <- 'time_to_resistance0.5'
    color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    #color <- 'exposure'

    print( ggplot(ggInsOuts, aes_string(x=i, y=y, color=color)) + 
             #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             geom_smooth(colour='red', linetype='dashed',size=0.5, show.legend=FALSE) +
             facet_wrap( ~ strategy) + #, show_guide = FALSE) + 
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i))
  }

## Looking more closely at ratio between the level of resistance to the first insecticide divided by that of the second one. Restricting the x axis to lower values.
## ?not very useful
```{r, eval=FALSE, echo=FALSE, warning=FALSE}

##
